---
title: "CE2"
author: "Nils, Jan, Rakesh, Benjamin"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(tidyverse)
library(httr)
library(rvest)
library(httr2)
```

# 1. Introduction

This report aims to answer the following research question:

*"Research question"*

# 2. Hypothesis

We try to perform a sentiment analysis on articles on Julien Assange. The articles were fetched from the Guardian API.

# 3. Code

## 3.1 Setting API Key up

We found several methods to set up the API key.

### 3.1.1 Version 1:
```{r, eval=FALSE}
# check wd
getwd()

# Create File using the windows editor
# Write on the first line without any space Key=Your_Key
# Note: Your_Key is the Key you got from the Guardians-API

# Call the file .Renviron it is already in the gitignore-file
# Note: When saving the file, check that you change the Data-Type

# Restart your R-Session

# Use this Code to read in your Key - It should appear in the Global Environment
api_key <- Sys.getenv(x= "Key")
```

### 3.1.2 Version 2:
```{r, eval=FALSE}
# Proposal of API key system and wrapper function to fetch data from the Guardian API.

# Save your API key in an api_credentials.csv file in the folder api_key. The column name the key is stored under must be named api_key. 

# Load the API key and store in a variable

api_key <- read_csv(here("api_key/api_credentials.csv")) %>% 
  pull(api_key)
```

### 3.1.3 Version 3:
```{r, eval=FALSE}
api_key <- rstudioapi::askForPassword()
```

## 3.2 Create a wrapper function to get the data from the API
```{r, eval=FALSE}
# Define the URL for the API
guardian_api_base_url <- "https://content.guardianapis.com/search"

# Create wrapper function to get the data from the API
get_guardian_data <- function(api_key, search_term, from_date, to_date, page) {
  
  # Define the parameters for the API call
    params <- list(
    "api-key" = api_key,
    "q" = search_term,
    "from-date" = from_date,
    "to-date" = to_date,
    "page" = page
  )
  
  # Make the API call
    response <- httr::GET(url = guardian_api_base_url, query = params)
  
  # Check if the API call was successful
    if (response$status_code == 200) {
    
    # Parse the response
        data <- httr::content(response)
    
    # Extract the relevant information
        results <- data$response$results
    
    # Return the results
        return(results)
    
  } else {
    
    # If the API call was not successful, print an error message
        message("Error: API call failed with status code ", response$status_code)
    
    # Return NULL
    return(NULL)
  }
}
```


# 4. Results

# 5. Discussion
